Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 README.Rmd
added to list back (so I don't forget anything)

>>>>

## To Do

- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Write up dataset descriptions in README and convert to a txt document for the submission
- Write up steps for creating the submission folder
- Update all files in the submission folder
- Consider getting rid of CyBox folder
- Delete old repo with long version
- Upload the files for submission, finish filling in questions, and submit!
